### 2016-03-15 chapters/intro.tex
Arbeit an der Introduction

Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL). In such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line. There are projects being developed feature-oriented, but don't have a feature model yet. This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.

Although the feature configuration gives  Developers the ability to create custom variants, there still has to be a consultant explaining the features to the customer, trying to figure out his current and future needs. As the Software grows and gets more features, this process gets more difficult, as you can no longer explain all the features, but you still have to figure out if the customer needs them or not.

This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.

\section*{Problem statement}
Very high complexity of configuration due to many features and constraints. Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.

\section*{Contribution}

Simplifying the process of configuration of product lines through extracting a feature model out of naming conventions and configuration files from an existing product line in FeatureIDE and applying a configuration wizard which guides the user though the creation of a specific product (variant) in the style of a questionnaire, thus applying the domain knowledge of an expert.

%This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.

>>>>

Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL). In such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line. There are projects being developed feature-oriented, but don't have a feature model yet. Implementing it on top of a given Project can result in a very complex task due to the amount of its features and the constraints between them. Additionally those informations are often already kept inside of readme- or configuration files, what predesignates it to be analyzed programmatically. This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.

Although the feature configuration gives  Developers the ability to create custom variants, there still has to be a consultant explaining the features to the customer, trying to figure out his current and future needs. As the Software grows and gets more features, this process gets more difficult, as you can no longer explain all the features, but you still have to figure out if the customer needs them or not. This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.

FeatureIDE being the leading open source IDE for feature-oriented-software development, it provides us with all the functionality needed to programatically generate and work with Feature Models. The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.

This work will demonstrate the named simplifications based on a real life Project. This software, an open source ERP System called "Odoo" [] is predestined to be developed feature-oriented due to a huge amount of features and complex constraints. The Project is currently being developed and structured feature oriented, although it doest't contain a Feature Model yet. Furthermore Odoo reached a critical amount of features where a salesman cannot consult a customer by going through all of the features anymore, but has to come up with a more effective way.

The paper is structured as follows. In section 2 we ... . Followed by section 3 where we ... . Then in section 4, ... . Finally we conclude and give an outlook for future works.
